taxize: taxonomic search and retrieval in R

### 2013-10-01 f1000_rev/taxize_ms.Rnw
lighter header

\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}
\usepackage{hyperref}
\usepackage{listings}

\lstset{
  language=R,
  basicstyle=\ttfamily,
  showstringspaces=false,
  breaklines=true,
  keywordstyle={\textit},
  %morekeywords={text},% list your attributes here, 
  escapechar=\&% char to escape out of listings and back to LaTeX
}

@@

<<setup, include=FALSE, cache=FALSE, size='scriptsize'>>=
## set global chunk options
opts_chunk$set(fig.align='center', fig.show='hold', par=TRUE, warning=FALSE, message=FALSE, error=FALSE, comment='#')
@

@@

<<resolvenames, cache=TRUE, size='scriptsize'>>=
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
temp[ , -c(1,4)]
@

@@

<<tnrs, cache=TRUE, size='scriptsize'>>=
mynames <- c("Helianthus annuus", "Pinus contort", "Poa anua", "Abis magnifica",
  	"Rosa california", "Festuca arundinace", "Sorbus occidentalos","Madia sateva")
tnrs(query = mynames)[ , -c(5:7)]
@

@@

<<synonyms, cache=TRUE, message=FALSE, warning=FALSE, size='scriptsize'>>=
library(plyr)
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus", "Helianthus annuus var. lenticularis", "Helianthus annuus var. macrocarpus", "Helianthus annuus var. texanus")
tsn <- get_tsn(mynames)
ldply(tsn, itis_acceptname)
@

@@

<<taxname, cache=TRUE, size='scriptsize'>>=
tax_name(query = "Helianthus annuus", get = "family", db = "itis")
tax_name(query = "Helianthus annuus", get = "family", db = "ncbi")
@

@@

<<interactive_many, cache=TRUE, size='scriptsize'>>=
splist <- c("annona cherimola", 'annona muricata', "quercus robur",
  	"shorea robusta", "pandanus patina", "oryza sativa", "durio zibethinus")
get_tsn(searchterm = splist, searchtype = "sciname")
@

@@

<<phylomaticphylogeny, eval=TRUE, dev=c ('pdf','jpeg'), dpi=300, out.width='4in', out.height='4in', cache=TRUE, include=FALSE, size='scriptsize'>>=
taxa <- c("Poa annua", "Abies procera", "Helianthus annuus")
tree <- phylomatic_tree(taxa = taxa)
tree$tip.label <- capwords(tree$tip.label)
plot(tree, cex=1)
@

@@

<<genbank_one, eval=TRUE, cache=TRUE, size='scriptsize'>>=
out <- get_genes_avail(taxon_name = "Umbra limi", seqrange = "1:2000", getrelated = FALSE)
@

>>>>

\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}
\usepackage{hyperref}

@@

<<setup, include=FALSE, cache=FALSE, size='scriptsize'>>=
## set global chunk options
options(width=58)
opts_chunk$set(fig.align='center', fig.show='hold', par=TRUE, warning=FALSE, message=FALSE, error=FALSE, comment='#')
@

@@

<<resolvenames, cache=TRUE, size='scriptsize', tidy=FALSE>>=
temp <- gnr_resolve(names = c("Helianthos annus", 
                              "Homo saapiens"))
temp[ , -c(1,4)]
@

@@

<<tnrs, cache=TRUE, size='scriptsize', tidy=FALSE>>=
mynames <- c("Helianthus annuus", "Pinus contort", 
             "Poa anua", "Abis magnifica", "Rosa california", 
             "Festuca arundinace", "Sorbus occidentalos",
             "Madia sateva")
tnrs(query = mynames)[ , -c(5:7)]
@

@@

<<synonyms, cache=TRUE, message=FALSE, warning=FALSE, size='scriptsize', tidy=FALSE>>=
library(plyr)
mynames <- c("Helianthus annuus ssp. jaegeri", 
             "Helianthus annuus ssp. lenticularis", 
             "Helianthus annuus ssp. texanus", 
             "Helianthus annuus var. lenticularis", 
             "Helianthus annuus var. macrocarpus", 
             "Helianthus annuus var. texanus")
tsn <- get_tsn(mynames)
ldply(tsn, itis_acceptname)
@

@@

<<taxname, cache=TRUE, size='scriptsize', tidy=FALSE>>=
tax_name(query = "Helianthus annuus", get = "family", 
         db = "itis")
tax_name(query = "Helianthus annuus", get = "family", 
         db = "ncbi")
@

@@

<<interactive_many, cache=TRUE, size='scriptsize', tidy=FALSE>>=
splist <- c("annona cherimola", 'annona muricata', 
            "quercus robur", "shorea robusta", 
            "pandanus patina", "oryza sativa", 
            "durio zibethinus")
get_tsn(searchterm = splist, searchtype = "sciname")
@

@@

<<phylomaticphylogeny, eval=TRUE, dev=c ('pdf','jpeg'), dpi=300, out.width='4in', out.height='4in', cache=TRUE, include=FALSE, size='scriptsize'>>=
taxa <- c("Poa annua", "Abies procera", "Helianthus annuus")
tree <- phylomatic_tree(taxa = taxa)
tree$tip.label <- capwords(tree$tip.label)
plot(tree, cex = 1)
@

@@

<<genbank_one, eval=TRUE, cache=TRUE, size='scriptsize', tidy=FALSE>>=
out <- get_genes_avail(taxon_name = "Umbra limi", 
                       seqrange = "1:2000", 
                       getrelated = FALSE)
@

### 2013-10-01 f1000_rev/taxize_ms.tex
lighter header

\usepackage{alltt}
\usepackage{f1000_styles}
\usepackage{hyperref}
\usepackage{listings}

\lstset{
  language=R,
  basicstyle=\ttfamily,
  showstringspaces=false,
  breaklines=true,
  keywordstyle={\textit},
  %morekeywords={text},% list your attributes here, 
  escapechar=\&% char to escape out of listings and back to LaTeX
}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{temp} \hlkwb{<-} \hlkwd{gnr_resolve}\hlstd{(}\hlkwc{names} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"Helianthos annus"}\hlstd{,} \hlstr{"Homo saapiens"}\hlstd{))}
\hlstd{temp[,} \hlopt{-}\hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{4}\hlstd{)]}
\end{alltt}
\begin{verbatim}
#                  matched_name       data_source_title
# 1        Helianthus annuus L.       Catalogue of Life
# 2            Helianthus annus GBIF Taxonomic Backbone
# 3            Helianthus annus                     EOL
# 4         Helianthus annus L.                     EOL
# 5            Helianthus annus           uBio NameBank
# 6 Homo sapiens Linnaeus, 1758       Catalogue of Life
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{mynames} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Helianthus annuus"}\hlstd{,} \hlstr{"Pinus contort"}\hlstd{,} \hlstr{"Poa anua"}\hlstd{,} \hlstr{"Abis magnifica"}\hlstd{,}
    \hlstr{"Rosa california"}\hlstd{,} \hlstr{"Festuca arundinace"}\hlstd{,} \hlstr{"Sorbus occidentalos"}\hlstd{,} \hlstr{"Madia sateva"}\hlstd{)}
\hlkwd{tnrs}\hlstd{(}\hlkwc{query} \hlstd{= mynames)[,} \hlopt{-}\hlkwd{c}\hlstd{(}\hlnum{5}\hlopt{:}\hlnum{7}\hlstd{)]}
\end{alltt}
\begin{verbatim}
#          submittedName        acceptedName    sourceId score
# 9    Helianthus annuus   Helianthus annuus iPlant_TNRS     1
# 10   Helianthus annuus   Helianthus annuus        NCBI     1
# 4        Pinus contort      Pinus contorta iPlant_TNRS  0.98
# 5             Poa anua           Poa annua iPlant_TNRS  0.96
# 3       Abis magnifica     Abies magnifica iPlant_TNRS  0.96
# 7      Rosa california    Rosa californica iPlant_TNRS  0.99
# 8      Rosa california          California        NCBI     1
# 2   Festuca arundinace Festuca arundinacea iPlant_TNRS  0.99
# 1  Sorbus occidentalos Sorbus occidentalis iPlant_TNRS  0.99
# 6         Madia sateva        Madia sativa iPlant_TNRS  0.97
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{splist} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"annona cherimola"}\hlstd{,} \hlstr{"annona muricata"}\hlstd{,} \hlstr{"quercus robur"}\hlstd{,} \hlstr{"shorea robusta"}\hlstd{,}
    \hlstr{"pandanus patina"}\hlstd{,} \hlstr{"oryza sativa"}\hlstd{,} \hlstr{"durio zibethinus"}\hlstd{)}
\hlkwd{get_tsn}\hlstd{(}\hlkwc{searchterm} \hlstd{= splist,} \hlkwc{searchtype} \hlstd{=} \hlstr{"sciname"}\hlstd{)}
\end{alltt}
\begin{verbatim}
# [1] "506198" "18098"  "19405"  "506787" "507376" "41976"  "506099"
# attr(,"class")
# [1] "tsn"
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\usepackage{alltt}
\usepackage{f1000_styles}
\usepackage{hyperref}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{temp} \hlkwb{<-} \hlkwd{gnr_resolve}\hlstd{(}\hlkwc{names} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"Helianthos annus"}\hlstd{,}
                              \hlstr{"Homo saapiens"}\hlstd{))}
\hlstd{temp[ ,} \hlopt{-}\hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,}\hlnum{4}\hlstd{)]}
\end{alltt}
\begin{verbatim}
#                  matched_name       data_source_title
# 1        Helianthus annuus L.       Catalogue of Life
# 2            Helianthus annus GBIF Taxonomic Backbone
# 3            Helianthus annus                     EOL
# 4         Helianthus annus L.                     EOL
# 5            Helianthus annus           uBio NameBank
# 6 Homo sapiens Linnaeus, 1758       Catalogue of Life
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{mynames} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Helianthus annuus"}\hlstd{,} \hlstr{"Pinus contort"}\hlstd{,}
             \hlstr{"Poa anua"}\hlstd{,} \hlstr{"Abis magnifica"}\hlstd{,} \hlstr{"Rosa california"}\hlstd{,}
             \hlstr{"Festuca arundinace"}\hlstd{,} \hlstr{"Sorbus occidentalos"}\hlstd{,}
             \hlstr{"Madia sateva"}\hlstd{)}
\hlkwd{tnrs}\hlstd{(}\hlkwc{query} \hlstd{= mynames)[ ,} \hlopt{-}\hlkwd{c}\hlstd{(}\hlnum{5}\hlopt{:}\hlnum{7}\hlstd{)]}
\end{alltt}
\begin{verbatim}
#          submittedName        acceptedName    sourceId
# 9    Helianthus annuus   Helianthus annuus iPlant_TNRS
# 10   Helianthus annuus   Helianthus annuus        NCBI
# 4        Pinus contort      Pinus contorta iPlant_TNRS
# 5             Poa anua           Poa annua iPlant_TNRS
# 3       Abis magnifica     Abies magnifica iPlant_TNRS
# 7      Rosa california    Rosa californica iPlant_TNRS
# 8      Rosa california          California        NCBI
# 2   Festuca arundinace Festuca arundinacea iPlant_TNRS
# 1  Sorbus occidentalos Sorbus occidentalis iPlant_TNRS
# 6         Madia sateva        Madia sativa iPlant_TNRS
#    score
# 9      1
# 10     1
# 4   0.98
# 5   0.96
# 3   0.96
# 7   0.99
# 8      1
# 2   0.99
# 1   0.99
# 6   0.97
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{splist} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"annona cherimola"}\hlstd{,} \hlstr{'annona muricata'}\hlstd{,}
            \hlstr{"quercus robur"}\hlstd{,} \hlstr{"shorea robusta"}\hlstd{,}
            \hlstr{"pandanus patina"}\hlstd{,} \hlstr{"oryza sativa"}\hlstd{,}
            \hlstr{"durio zibethinus"}\hlstd{)}
\hlkwd{get_tsn}\hlstd{(}\hlkwc{searchterm} \hlstd{= splist,} \hlkwc{searchtype} \hlstd{=} \hlstr{"sciname"}\hlstd{)}
\end{alltt}
\begin{verbatim}
# [1] "506198" "18098"  "19405"  "506787" "507376" "41976" 
# [7] "506099"
# attr(,"class")
# [1] "tsn"
\end{verbatim}
\end{kframe}
\end{knitrout}
